Enhanced Global PTM Discovery (G-PTM-D) with MetaMorpheus

### 2018-02-16 paper.tex
jkjf

The database augmentation step allowed 208 modification types, including PTMs, adducts, and chemical modifications.
See supplement Supp1 for a complete listing.

@@

A critical parameter for peptide identification is mass accuracy\citep{Scherl_2008}.
Higher mass accuracy provides increased specificity and thus confidence in peptide identifications, decreasing the false discovery rate.
Instrument noise, systematic drift and miscalibration all limit the mass accuracy in acquired spectra.
Multiple calibration strategies to improve mass accuracy have been devised and fall into three general categories: external calibration prior to the MS experiment (e.g. standard instrument calibration protocols); internal calibration during the MS experiment (e.g. real-time calibration using a lock mass standard\citep{Olsen_2005}); and spectral calibration subsequent to the MS experiment (post-acquisition spectral calibration).
We developed a post-acquisition calibration procedure that builds upon the software lock mass concept\citep{Cox_2011} recently reported by the Mann group.
In our strategy, the m/z differences between expected and observed peaks in the peptide tandem MS spectra are compiled, and then used to recalibrate the spectra.
The spectral calibration procedure consists of two steps: Step 1: A narrow tolerance (e.g. 10 ppm precursor, 20 ppm fragment) database search is performed on the dataset.
This yields a set of peptide identifications subject to a desired FDR.
Step 2: The identifications from Step 1 provide a theoretical list of m/z peaks that should match closely to observed m/z peaks in the spectra file, and the discrepancies between the theoretical and observed peaks are used to inform a peak shifting procedure.
The calibration algorithm is described in detail in Document S-2.

@@

The following files are available free of charge.
\begin{itemize}
  \item Supp1.xlsx: The complete list of modifications used for enhanced G-PTM-D
  \item Supp2Calibration.docx: brief description
\end{itemize}

>>>>

The database augmentation step allowed 208 modification types, including PTMs, adducts, and chemical modifications.
See Table S1 for a complete listing.

@@

A critical parameter for peptide identification is mass accuracy\citep{Scherl_2008}.
Higher mass accuracy provides increased specificity and thus confidence in peptide identifications, decreasing the false discovery rate.
Instrument noise, systematic drift and miscalibration all limit the mass accuracy in acquired spectra.
Multiple calibration strategies to improve mass accuracy have been devised and fall into three general categories: external calibration prior to the MS experiment (e.g. standard instrument calibration protocols); internal calibration during the MS experiment (e.g. real-time calibration using a lock mass standard\citep{Olsen_2005}); and spectral calibration subsequent to the MS experiment (post-acquisition spectral calibration).
We developed a post-acquisition calibration procedure that builds upon the software lock mass concept\citep{Cox_2011} recently reported by the Mann group.
In our strategy, the m/z differences between expected and observed peaks in the peptide tandem MS spectra are compiled, and then used to recalibrate the spectra.
The spectral calibration procedure consists of two steps: Step 1: A narrow tolerance (e.g. 10 ppm precursor, 20 ppm fragment) database search is performed on the dataset.
This yields a set of peptide identifications subject to a desired FDR.
Step 2: The identifications from Step 1 provide a theoretical list of m/z peaks that should match closely to observed m/z peaks in the spectra file, and the discrepancies between the theoretical and observed peaks are used to inform a peak shifting procedure.
The calibration algorithm is described in detail in Document S1.

@@

The following supplementary information is available:
\begin{itemize}
  \item Table S1: The complete list of modifications used for enhanced G-PTM-D
  \item Document S1: A brief description of the calibration methodology
  \item Document S2: A 
\end{itemize}
